### 2025-07-10 index.qmd
20250710 - factor analysis

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "broom", "broom.mixed", 
  "psych", "downlit", "xml2", "nflreadr", "nflplotR", "nflfastR", "nflseedR", 
  "nfl4th", "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", 
  "XICOR", "dagitty", "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", 
  "grid", "patchwork", "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", 
  "pbkrtest", "sjstats", "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", 
  "fitdistrplus", "sn", "mclust", "magrittr", "viridis", "viridisLite", "msir", 
  "plotly", "webshot2", "quantmod", "fPortfolio", "NMOF", "nFactors", "xts", 
  "zoo", "forecast", "stringi", "parallelly", "doParallel", "missRanger", 
  "ggridges", "powerjoin", "caret", "tidymodels", "LongituRF", "gpboost", 
  "cmdstanr", "corrplot", "correlation", "mgcv", "rms", "car", "performance", 
  "lavaan", "lavaangui", "mice", "miceadds", "interactions", "robustbase", 
  "ordinal", "MASS", "data.table", "future", "future.apply", "see", "SimDesign", 
  "effectsize", 
  "learnr", "remotes", "shiny", "PearsonDS" # packages that are cited but not used for computation (and thus do not need to be installed by me or readers)
)

>>>>

# Packages to drop: stringi (replace with stringr from tidyverse); caret (replace with tidymodels)

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "broom", "broom.mixed", "psych", "downlit", "xml2", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", "fitdistrplus", "sn", 
  "mclust", "magrittr", "viridis", "viridisLite", "msir", "plotly", "webshot2", 
  "quantmod", "fPortfolio", "NMOF", "nFactors", "xts", "zoo", "forecast",
  "stringi", "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", 
  "caret", "LongituRF", "gpboost", "cmdstanr", "corrplot", "mgcv", "rms", 
  "car", "lavaan", "lavaanPlot", "mice", "miceadds", "interactions", 
  "robustbase", "ordinal", "MASS", "data.table", "future", "future.apply", 
  "SimDesign", "domir",
  "tidyverse", "ggplot2", "dplyr", "lubridate", # packages that are part of the tidyverse ecosystem
  "nflverse", "nflfastR", "nflseedR", "nfl4th", "nflreadr", "nflplotR", # packages that are part of the nflverse ecosystem
  "tidymodels", "rsample", "parsnip", "recipes", "tune", "yardstick", # packages that are part of the tidymodels ecosysyem
  "easystats", "see", "performance", "parameters", "correlation", "effectsize", # packages that are part of the easystats ecosystem
  "learnr", "remotes", "shiny", "PearsonDS", "lavaangui" # packages that are cited but not used for computation (and thus do not need to be installed by me or readers)
)
